Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r}
histo(mix_data_1, paste0("Campuran 1"), color="#792b9a")
```

```{r fig.height=3.5, fig.width=6*4, dpi=300}
histo <- function(dist, title, color){
  df <- data.frame(x = dist)

@@

atas <- c(
  histo(norm_data, paste0("Normal"), color="#357a87"),
  histo(mix_data_1, paste0("Campuran 1"), color="#792b9a"),
  histo(mix_data_2, paste0("Campuran 2"), color="#96336c"),
  histo(mix_data_3, paste0("Campuran 3"), color="#9a3b1a")  
)
atas <- plot_grid(plotlist = atas, ncol = 4)
atas
```

```{r fig.height=3.5*4, fig.width=6*4, dpi=300}

plot_grid(atas, all_plots, ncol = 8)
```

```{r fig.height=3.5*4, fig.width=6*4, dpi=300}
plot_distribution2 <- function(data_rataan, title, color) {
  df_rataan <- data.frame(x = data_rataan)

@@

plot_grid(plotlist = all_plots, ncol = 8)
```

>>>>

```{r fig.height=3.5*5, fig.width=6*4, dpi=300}
# Plot atas
histo <- function(dist, title, color){
  df <- data.frame(x = dist)

@@

atas <- c(
  histo(norm_data, paste0("Normal"), color="#357a87"),
  histo(mix_data_1, paste0("Campuran 1"), color="#792b9a"),
  histo(mix_data_2, paste0("Campuran 2"), color="#96336c"),
  histo(mix_data_3, paste0("Campuran 3"), color="#9a3b1a")  
)

plot_grid_top <- plot_grid(plotlist = atas, ncol = 4)

# Plot bawah
plot_distribution2 <- function(data_rataan, title, color) {
  df_rataan <- data.frame(x = data_rataan)

@@

plot_grid_bottom <- plot_grid(plotlist = all_plots, ncol = 8)

# Gabung
plot_grid(plot_grid_top, plot_grid_bottom, ncol=1, rel_heights = c(0.2, 1))
```
